---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nterval `r utils::packageVersion("nterval")`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/nterval)](https://CRAN.R-project.org/package=nterval)
<!-- badges: end -->

The goal of nterval is to provide an approach for calculating the minimum required sample size for
estimation of population coverage intervals (e.g., k-sigma intervals).

## Installation

Install the package using `devtools`:

```{r, echo = TRUE, eval = FALSE}
# To install the most recent stable release of the package from Github
devtools::install_github("dygobeng/nterval@*release")

# To install the latest (development) version of the package from Github
devtools::install_github("dygobeng/nterval")
```

## Definitions

Before exploring an example, a few definitions:

* The **target coverage** is the expected proportion of a Normally-distributed population that 
should be contained within the k-sigma parametric sample interval (e.g., a 3-sigma sample interval
is expected to cover 99.73% of Normally-distributed observations).

* The **sample coverage** is the proportion of a Normally-distributed population that _is_ contained
within the k-sigma interval estimated using a sample from the population.

* The **upper and lower proximity limits** define the distance from the target coverage that an
individual sample's coverage can fall and still be considered "reasonably close" to the target. 
These bounds are useful for dialing acceptable 
  
  + _producer's risk_ by ensuring that the lower proximity limit does not move so low as to result
  in an unacceptable false positive rate (probability of flagging common cause variation), and
  
  + _consumer's risk" by ensuring that the upper proximity limit does not move so high as to result
  in an unacceptable false negative rate (probability of failing to flag special cause variation)

* The **reliability** is the proportion of individual sample coverages expected to fall within the
proximity limits.

## Example

A researcher would like to determine the minimum sample size required to provide that a 2-sigma
sample interval (with a targeted coverage of 95.44% when calculated using data that can be 
reasonably approximated by a Normal distribution) will cover no less than 93% of the population and
no more than 97% of the population with 70% reliability. 

We'll use the `find_n_ksigma()` function to determine the required sample size. The main arguments
accept values for `k` (based on the target coverage), the `proximity_range`, and the targeted
`reliability`:

```{r}

```

